Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-30 prop_letter.tex
From: Tai, Yu-Tsung Sent: Thursday, March 30, 2017 1:41 To: Hanson, Andrew J. <hansona@indiana.edu> Subject: RE: a talk might be of interest to your department
How about something like this?
===
Textbook quantum mechanics asserts that the probability of a measurement
can be computed from wave function of the system and the measuring
observable \emph{exactly} while real measurements must be finite
precision.
Whether finite precision measurement in reality affect the idealized
quantum concept, e.g.,
contextuality~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
and the very foundation of q

The tension between finite precision measurement and the foundation
of quantum mechanics sharpened, when the original definition of contextuality
based on infinitely precised numbers is proved not experimental verifiable~\cite{PhysRevLett.83.3751,Kent1999}.
After a long debate~\cite{Mermin1999,Peres2003,BarrettKent2004},
people are still trying to update the definition of contextuality
when they want to perform further experiments~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

We found that finite precision measurement affects not only contextuality
but also the fundamental rule computing probability from a state.
In the early formulation of quantum mechanics, von Neumann essentially
formulated a quantum state as a density matrix while Mackey formulated
a quantum state as a quantum probability measure which are proved
by Gleason to be the essentially same as a density matrix~\cite{Varadarajan2008}.
Combining quantum probability measures and the classical IVPM~\cite{JamisonLodwick2004}
which could be used to formulate classical finite precision measurement,
we can define quantum IVPMs. Surprisingly, there is a quantum IVPM
which cannot be compatible with any density matrix according to the
Born rule. Similar to revising the definition of contextuality because
of finite precision measurement, the very basic definition of a quantum
state or how to compute the probability from a state might need to
be refined when we consider the finite precision measurement. This
can also provides a new quantum phenomena different from the classical
world, because IVPMs become classical so that the non-Born IVPMs disappears
when we restricting the domain of quantum IVPMs on a commuting sub-event
space. \newpage{}

>>>>

The tension between finite precision measurement and the foundation
of quantum mechanics sharpened, when the original definition of contextuality
based on infinitely precise numbers is proved not experimental verifiable~\cite{PhysRevLett.83.3751,Kent1999}.
After a long debate~\cite{Mermin1999,Peres2003,BarrettKent2004},
people are still trying to update the definition of contextuality
when they want to perform further experiments~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

We found that finite precision measurement affects not only contextuality
but also the fundamental rule computing probability from a state.
In the early formulation of quantum mechanics, von Neumann essentially
formulated a quantum state as a density matrix while Mackey formulated
a quantum state as a quantum probability measure which are proved
by Gleason to be the essentially same as a density matrix~\cite{Varadarajan2008}.
Combining quantum probability measures and the classical IVPM~\cite{JamisonLodwick2004}
which could be used to formulate classical finite precision measurement,
we can define quantum IVPMs. Surprisingly, there is a quantum IVPM
which cannot be compatible with any density matrix according to the
Born rule. Similar to revising the definition of contextuality because
of finite precision measurement, the very basic definition of a quantum
state or how to compute the probability from a state might need to
be refined when we consider the finite precision measurement. This
can also provide a new quantum phenomena different from the classical
world, because IVPMs become classical so that the non-Born IVPMs disappears
when we restricting the domain of quantum IVPMs on a commuting sub-event
space. \newpage{}
